Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-10-29 paper/paper.tex
changes to movie scripts and small changes to text of paper Tested everything on crystal.

As described in Section~\ref{sec:model-method-shapes}, we will focus
on simulation of four illustrative flattened cell shapes: two shapes
created to replicate those shapes observed experimentally by
Mannik~\cite{mannik2012robustness} (shape~\emph{A} and
shape~\emph{B}), and for comparison two symmetrical stadium shapes
that have the identical aspect ratio, thickness and volume (stadium
\emph{A} and stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.
These stadium shapes enable us to distinguish between the effect of
cellular shape irregularity and assymetry, and that of overall size
and aspect ratio.  We note that shape \emph{B} is more irregular than
shape \emph{A}, and in particular features a prominant region of
concavity on its left-hand side.  For each of these shapes (in
addition to the wild-type pill shape discussed previously) we have
simulated in excess of 15000 seconds (over four hours) of evolution of
the MinD system using the deterministic version of Huang's
model~\cite{huang2003dynamic}, and much more than this using the
stochastic model. \fixme{is this sentence ok?}

@@

However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
cell shape irregularity versus overall size and aspect ratio in
developing an understanding of the origin of the experimentally
observed behavior.  Although in the movies the stadiums appear to
display, on average over long time scales, a more regular bipolar
oscillation than the irregular mannik shapes, the limited time range
of the arrow plots (350 seconds) is inadequate when studying this
difference in behavoir.  We therefore return to the correlation
function between the number of proteins in a segment at the top of the
cell and the number of proteins in a segment at the bottom of the
cell.  For each shape we computed these correlation functions using
the entirety of our over 15000 seconds of simulation
data. Fig.~\ref{fig:corr-pancake-A} shows this plot for shape \emph{A}
and stadium \emph{A}.  E. Coli cell doubling times vary widely
depending on environmental conditions, but will often be between 20
minutes to 100 minutes~\cite{pierucci1972chromosome}, while
flourescent microscopy experiments have shown that the FtsZ ring
builds itself with a half life of roughly 30
seconds~\cite{stricker2002rapid}.  Here we plot correlations of
correlation times up to 600 seconds, a biologically relevent
timescale.

>>>>

As described in Section~\ref{sec:model-method-shapes}, we will focus
on simulation of four illustrative flattened cell shapes: two shapes
created to replicate those shapes observed experimentally by
Mannik~\cite{mannik2012robustness} (shape~\emph{A} and
shape~\emph{B}), and for comparison two symmetrical stadium shapes
that have the identical aspect ratio, thickness and volume (stadium
\emph{A} and stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.
These stadium shapes enable us to distinguish between the effect of
cellular shape irregularity and assymetry, and that of overall size
and aspect ratio.  We note that shape \emph{B} is more irregular than
shape \emph{A}, and in particular features a prominant region of
concavity on its left-hand side.  For each of these shapes (in
addition to the wild-type pill shape discussed previously) we have
simulated in excess of 15000 seconds (over 4 hours) of evolution of
the MinD system using the deterministic version of Huang's
model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
27 hours) using the stochastic model.

@@

However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
cell shape irregularity versus overall size and aspect ratio in
developing an understanding of the origin of the experimentally
observed behavior.  Although in the movies the stadiums appear to
display, on average over long time scales, a more regular bipolar
oscillation than the irregular mannik shapes, the limited time range
of the arrow plots (350 seconds) is inadequate when studying this
difference in behavoir.  We therefore return to the correlation
function between the number of proteins in a segment at the top of the
cell and the number of proteins in a segment at the bottom of the
cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for shape
\emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
widely depending on environmental conditions, but will often be
between 20 minutes to 100 minutes~\cite{pierucci1972chromosome}, while
flourescent microscopy experiments have shown that the FtsZ ring
builds itself with a half life of roughly 30
seconds~\cite{stricker2002rapid}.  Here we plot correlations of
correlation times up to 600 seconds, a biologically relevent
timescale.
